Kids health and child data cleaning

### 2020-02-28 child_health_data_cleaning.Rmd
data cleaning updates

# write_rds(kids_med_visit, "Output/kids_med_visit.rds")
```

@@

@@

################# CSQ  ###############

@@

>>>>

# write_rds(kids_med_visit, "Output/kids_med_visit.rds")

save_var_names <- data.frame(t(kids_med_visit)) %>% 
  rownames_to_column() %>% 
  select(rowname)

write_csv(save_var_names, "Output/medvisit_var_names.csv")
```

@@

# Waiting on files from NN and AK

save_var_names <- data.frame(t(wmt_birthinfancy_initial)) %>% 
  rownames_to_column() %>% 
  select(rowname)

write_csv(save_var_names, "Output/birthinfancy_var_names.csv")
```

@@

################# CSQ - child symptom questionnaire  ###############

@@

# Waiting on files from NN and AK

save_var_names <- data.frame(t(wmt_csq_initial)) %>% 
  rownames_to_column() %>% 
  select(rowname)

write_csv(save_var_names, "Output/csq_var_names.csv")
```
